% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 12
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 12.a, 12.b, etc.
\renewcommand{\thepage}{12.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  וְאָהַבְתָּ אֶת יְיָ אֱלֹהֶיךָ \\
בְּכָל־לְבָבְךָ וּבְכָל־נַפְשְׁךְ וּבְכָל־ \\
מְאֹדֶךָ: וְהָיוּ הַדְּבָרִים הָאֵלֶּה \\
אֲשֶׁר אָנֹכִי מְצַוּךְ הַיּוֹם עַל־ \\
לְבָבֶךָ: וְשִׁנַּנְתָּם לְבָנֶיךָ וְדִבַּרְתָּ \\
בָּם בְּשִׁבְתְּךָ בְּבֵיתֶךָ וּבְלֶכְתְּךָ \\
בַדֶּרֶךְ וּבְשָׁכְבְּךָ וּבְקוּמֶךְ: \\
T \\
וּקְשַׁרְתָּם לְאוֹת עַל־יָדֶךְ וְהָיוּ \\
לְטְטָפְת בֵּין עֵינֶיךָ: וּכְתַבְתָּם \\
עַל־מְחֲזוֹת בֵּיתֶךָ וּבִשְׁעָרֶיךָ: \\
ለ \\
לְמַעַן תִּזְכְּרוּ וַעֲשִׂיתֶם אֶת־ \\
כָּל־מִצְוֹתָי וִהְיִיתֶם קְדֹשִׁים \\
לֵאלֹהֵיכֶם: אֲנִי יְיָ אֱלֹהֵיכֶם \\
אֲשֶׁר הוֹצֵאתִי אֶתְכֶם מֵאֶרֶץ \\
מִצְרַיִם לִהְיוֹת לָכֶם לֵאלֹהִים \\
אֲנִי יְיָ אֱלֹהֵיכֶם: \\
>> \\
T:%
}

\newcommand{\blockB}{%
  V'AHAVTA et Adonai Elohecha, \\
b'chol l'vav'cha uv'chol nafsh'cha uv'chol \\
m'odecha. V'hayu had'varim ha-eileh \\
asher anochi m'tzav'cha hayom al \\
I'vavecha. V'shinantam l'vanecha v'dibarta \\
bam b'shivt'cha b'veitecha uv'lecht'cha \\
vaderech uv'shochb'cha uv'kumecha. \\
Uk'shartam l'ot al yadecha v'hayu \\
l'totafot bein einecha. Uch'tavtam \\
al m'zuzot beitecha uvisharecha. \\
I'maan tizk'ru vaasitem et \\
kol mitzvotai vih'yitem k'doshim \\
l'Eloheichem. Ani Adonai Eloheichem, \\
asher hotzeiti et-chem mei-eretz \\
Mitzrayim lih'yot lachem l'Elohim \\
ani Adonai Eloheichem.%
}

\newcommand{\blockC}{%
  YOU SHALL LOVE Adonai your God with all your heart, \\
with all your soul, and with all your might. \\
Take to heart these instructions with which I charge you this day. \\
Impress them upon your children. \\
Recite them when you stay at home and when you are away, \\
when you lie down and when you get up. \\
Bind them as a sign on your hand and let them serve as a symbol on your \\
inscribe them on the doorposts of your house and on your gates. \\
Thus you \\
shall remember to observe all My commandments \\
and to be holy to your God. \\
I am Adonai, your God, who brought you out of the land of Egypt to be \\
I am Adonai your God. \\
» \\
יְיָ אֱלֹהֵיכֶם אֱמֶת. \\
T: \\
Adonai Eloheichem EMET. \\
forehead; \\
your \\
God:%
}

\newcommand{\blockD}{%
  For those who choose: At the end of the Shma, after the words Eloheichem, the word emet ("true") is added as an immediate affirmation of its truth. \\
V'ahavta... You shall love... Deuteronomy 6:5-9 \\
L'maan tizkru... Thus you shall remember... Numbers 15:40-41%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}