% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 122
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 122.a, 122.b, etc.
\renewcommand{\thepage}{122.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  וַיְהִי עֶרֶב וַיְהִי בְקֶר \\
יוֹם הַשְּׁשִׁי.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  VAY'HI EREV vay'hi voker \\
yom hashishi.%
}

\newcommand{\blockC}{%
  AND THERE WAS EVENING and there was morning, \\
the sixth day.%
}

\newcommand{\blockD}{%
  \begin{hebrew}
  וַיְכַלּוּ הַשָּׁמַיִם וְהָאָרֶץ \\
וְכָל־צְבָאָם. \\
וַיְכַל אֱלֹהִים בַּיּוֹם הַשְּׁבִיעִי \\
מְלַאכְתּוֹ אֲשֶׁר עָשָׂה. \\
וַיִּשְׁבֹּת בַּיּוֹם הַשְּׁבִיעִי \\
מִכָּל־מְלַאכְתּוֹ אֲשֶׁר עָשָׂה. \\
וַיְבָרֶךְ אֱלֹהִים אֶת־יוֹם הַשְּׁבִיעִי \\
וַיְקַדַּשׁ אֹתוֹ, כִּי בוֹ שָׁבַת מִכָּל־ \\
מְלַאכְתּוֹ אֲשֶׁר בָּרָא אֱלֹהִים לַעֲשׂוֹת.
  \end{hebrew}%
}

\newcommand{\blockE}{%
  VAY'CHULU hashamayim v'haaretz \\
v'chol tz'vaam. \\
Vay'chal Elohim bayom hashvi-i \\
m'lachto asher asah. \\
Vayishbot bayom hashvi-i \\
mikol m'lachto asher asah. \\
Vay'varech Elohim et yom hashvi-i \\
vay'kadeish oto ki vo shavat mikol \\
m'lachto asher bara Elohim laasot.%
}

\newcommand{\blockF}{%
  THE HEAVEN AND THE EARTH were finished, and all their array. \\
On the seventh day God finished the work that God had been doing, \\
and God ceased on the seventh day from all the work that God had done. \\
And God blessed the seventh day and declared it holy, \\
because on it God ceased from all the work of creation that God had done.%
}

\newcommand{\blockG}{%
  Shabbat Kiddush -The beginning of Shabbat is marked by reciting a benediction sanctifying \\
the day (Kiddush HaYom or K'dushat HaYom, "Sanctification of the Day"; M. B'rachot 8:1 and \\
P'sachim 10:2). The benediction praises God for the gift of Shabbat that marks Israel as unique. \\
Since Kiddush is recited over a cup of wine, symbolizing joy, it is preceded by the wine \\
benediction, borei pri hagafen, "Creator of the fruit of the vine." \\
Vayhi erev... And there was evening... Genesis 1:31 \\
Vay'chulu... The heaven and the earth... Genesis 2:1-3%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\blockG
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}