% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 128
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 128.a, 128.b, etc.
\renewcommand{\thepage}{128.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  הִנֵּה מַה־טוֹב וּמַה־נָעִים \\
שבת אַחִים גַּם־יָחַד.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  HINEIH MAH TOV \\
Hineih mah tov u'mah na-im \\
shevet achim gam yachad. \\
How good and how pleasant it is that brothers and sisters dwell together. \\
(Psalm 133:1)%
}

\newcommand{\blockC}{%
  \begin{hebrew}
  מַה יָפֶה הַיּוֹם, שַׁבָּת שָׁלוֹם.
  \end{hebrew}%
}

\newcommand{\blockD}{%
  MAH YAFEH HAYOM \\
Mah yafeh hayom, Shabbat shalom. \\
How lovely today is, Shabbat Shalom.%
}

\newcommand{\blockE}{%
  \begin{hebrew}
  יְדִיד נֶפֶשׁ, אָב הָרַחֲמָן, \\
מְשׁוֹךְ עַבְדְּךָ אֶל רְצוֹנֶךָ. \\
יָרוּץ עַבְדְּךָ כְּמוֹ אַיָּל, \\
יִשְׁתַּחֲוֶה אֶל מוּל הֲדָרֶךְ.
  \end{hebrew}%
}

\newcommand{\blockF}{%
  Y'DID NEFESH \\
Y'did nefesh, av harachaman, \\
m'shoch avd'cha el r'tzonecha. \\
Yarutz avd'cha k'mo ayal, \\
yishtachaveh el mul hadarecha. \\
 \\
Heart's delight, Source of mercy, draw Your servant into Your arms: \\
I leap like a deer to stand in awe before You.%
}

\newcommand{\blockG}{%
  \begin{hebrew}
  הַחַמָּה מֵרֹאשׁ הָאִילָנוֹת נִסְתַּלְקָה, \\
בְּאוּ וְנֵצֵא לִקְרַאת שַׁבָּת הַמַּלְכָּה. \\
הִנֵּה הִיא יוֹרֶדֶת, הַקְדוֹשָׁה הַבְּרוּכָה. \\
וְעִמָּהּ מַלְאָכִים, צְבָא שָׁלוֹם וּמְנוּחָה. \\
בְּאִי בְּאִי הַמַּלְכָּה, בְּאִי בְּאִי הַכַּלָּה. \\
שָׁלוֹם עֲלֵיכֶם, מַלְאֲכֵי הַשָּׁלוֹם.
  \end{hebrew}%
}

\newcommand{\blockH}{%
  SHABBAT HAMALKAH \\
 \\
Hachamah meirosh ha-ilanot nistalkah, \\
bo-u v'neitzei likrat Shabbat hamalkah. \\
Hinei hi yoredet, hak'doshah hab'ruchah. \\
V'imah malachim, tz'va shalom um'nuchah. \\
Bo-i bo-i hamalkah, bo-i bo-i hakalah. \\
Shalom aleichem, malachei hashalom. \\
 \\
The sun on the treetops no longer is seen; \\
come, gather to welcome the Sabbath, our queen. \\
Behold her descending, the holy, the blessed, \\
and with her the angels of peace and of rest. \\
Draw near, draw near, and here abide, \\
draw near, draw near, O Sabbath bride. \\
Peace also to you, you angels of peace.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\blockG
\vspace{1em}
% \newpage % Uncomment to break page here

\blockH
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}