% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 129
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 129.a, 129.b, etc.
\renewcommand{\thepage}{129.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  דּוֹדִי לִי וַאֲנִי לוֹ הָרֹעֶה בַּשׁוֹשַׁנִּים. \\
מִי זֹאת עֹלָה מִן־הַמִּדְבָּר, \\
מְקֶטֶרֶת מוֹר וּלְבוֹנָה \\
לִבַּבְתִּנִי, אֲחֹתִי כַלָּה. \\
עוּרִי צָפוֹן וּבוֹאִי תֵימָן
  \end{hebrew}%
}

\newcommand{\blockB}{%
  \begin{hebrew}
  קוֹל דּוֹדִי הִנֵּה זֶה־בָּא, \\
מְדַלֵּג עַל־הֶהָרִים, \\
מְקַפֵּץ עַל־הַגְּבָעוֹת.
  \end{hebrew}%
}

\newcommand{\blockC}{%
  \begin{hebrew}
  כִּי אֶשְׁמְרָה שַׁבָּת אֵל יִשְׁמְרֵנִי. \\
אוֹת הִיא לְעוֹלְמֵי עַד בֵּינוֹ וּבֵינִי.
  \end{hebrew}%
}

\newcommand{\blockD}{%
  \begin{hebrew}
  אֵלֶּה חָמְדָה לִבִּי, \\
חוּסָה כָּא וְאַל נָא תִּתְעַלָם.
  \end{hebrew}%
}

\newcommand{\blockE}{%
  Dodi li vaani lo haro-eh bashoshanim. \\
Mi zot olah min hamidbar, \\
M'kuteret mor ul'vonah . . . \\
Libavtini achoti chalah. \\
Uri tzafon uvo-i teiman ... \\
DODI LI \\
My beloved is mine and I am my beloved's who browses among the lilies. \\
Who is this that comes up from the desert, in clouds of myrrh and frankincense? \\
You have captured my heart, my sister, my bride. \\
Awake, O north wind, come, O south wind! \\
(Song of Songs 2:16; 3:6; 4:9, 16)%
}

\newcommand{\blockF}{%
  Kol dodi hinei zeh ba, \\
midaleig al heharim, \\
KOL DODI \\
m'kapeitz al hag'vaot. \\
Hark! My beloved comes leaping over the mountains, bounding over the hills. \\
(Song of Songs 2:8)%
}

\newcommand{\blockG}{%
  KI ESHM'RAH SHABBAT \\
Ki eshm'rah Shabbat El yishm'reini. \\
Ot hi l'olmei ad beino uveini. \\
When I keep Shabbat, God watches over me. It is a sign forever between God and me.%
}

\newcommand{\blockH}{%
  Eileh chamdah libi, \\
chusah na v'al na titalam. \\
EILEH CHAMDAH LIBI \\
God is my heart's desire. Appear! Do not hide.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\blockG
\vspace{1em}
% \newpage % Uncomment to break page here

\blockH
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}