% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 130
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 130.a, 130.b, etc.
\renewcommand{\thepage}{130.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  קַבָּלַת שַׁבָּת \\
KABBALAT SHABBAT - WELCOMING SHABBAT \\
This section, until Shalom Aleichem on page 142, does not offer alternative readings. \\
PSALM 95:1-7%
}

\newcommand{\blockB}{%
  \begin{hebrew}
  לְכוּ גְרַנְנָה לַייָ, \\
נָרִיעָה לְצוּר יִשְׁעֵנוּ. \\
נְקַדְמָה פָנָיו בְּתוֹדָה, \\
בִּזְמִרוֹת נָרִיעַ לוֹ. \\
כִּי אֵל גָּדוֹל יְיָ, \\
וּמֶלֶךְ גָּדוֹל עַל־כָּל־אֱלֹהִים. \\
אֲשֶׁר בְּיָדוֹ מֶחְקְרֵי אָרֶץ, \\
וְתוֹעֲפוֹת הָרִים לוֹ. \\
אֲשֶׁר־לוֹ הַיָּם וְהוּא עָשָׂהוּ, \\
וְיַבֶּשֶׁת יָדָיו יָצָרוּ. \\
בְּאוּ נִשְׁתַּחֲוֶה וְנִכְרָעָה \\
נִבְרְכָה לִפְנֵי־יְיָ עֹשֵׂנוּ. \\
כִּי־הוּא אֱלֹהֵינוּ, \\
וַאֲנַחְנוּ עַם מַרְעִיתוֹ וְצֹאן יָדוֹ, \\
הַיּוֹם אִם־בְּקֹלוֹ תִשְׁמָעוּ.
  \end{hebrew}%
}

\newcommand{\blockC}{%
  L'CHU n'ran'na l'Adonai, \\
nariyah l'tzur yisheinu. \\
N'kadmah fanav b'todah, \\
bizmirot naria lo. \\
Ki El gadol Adonai, \\
uMelech gadol al kol elohim. \\
Asher b'yado mech'k'rei aretz, \\
v'to-afot harim lo. \\
Asher lo hayam v'hu asahu, \\
v'yabeshet yadav yatzaru. \\
Bo-u nishtachaveh v'nichraah, \\
nivr'cha lifnei Adonai oseinu. \\
Ki hu Eloheinu, \\
vaanachnu am marito v'tzon yado. \\
Hayom im b'kolo tishma-u.%
}

\newcommand{\blockD}{%
  COME, LET US SING joyously to Adonai, \\
raise a shout for our Rock and Deliverer; \\
let us come into God's presence with praise; \\
let us raise a shout for God in song! \\
For Adonai is a great God, \\
the great ruler of all divine beings.%
}

\newcommand{\blockE}{%
  Kabbalat Shabbat, "Welcoming Shabbat," is one of the ritual innovations of the \\
circle of Kabbalists (Jewish mystics) who gathered around Rabbi Isaac Luria in sixteenth-century \\
Safed in the Land of Israel. \\
Psalms 95-99, 29 — This cycle of six psalms, representing the six days of creation, enjoins all \\
creation to sing out the praises of God. God's creative power is revealed in the world around us; \\
God's sovereignty is over all nature and all nations.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}