% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 132
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 132.a, 132.b, etc.
\renewcommand{\thepage}{132.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  SING TO ADONAI a new song, \\
sing to Adonai, all the earth. \\
Sing to Adonai, bless God's name, \\
proclaim God's victory day after day. \\
Tell of God's glory among the nations, \\
God's wondrous deeds, among all peoples. \\
For Adonai is great and much acclaimed, \\
God is held in awe by all divine beings. \\
All the gods of the peoples are mere idols, \\
but Adonai made the heavens. \\
Glory and majesty are before God; \\
strength and splendor are in God's temple. \\
Let the heavens rejoice and the earth exult; \\
let the sea and all within it thunder, \\
the fields and everything in them exult; \\
then shall all the trees of the forest shout for joy \\
at the presence of Adonai, for God is coming, \\
for God is coming to rule the earth; \\
God will rule the world justly, \\
and its peoples in faithfulness.%
}

\newcommand{\blockB}{%
  \begin{hebrew}
  מָלָךְ, תָּגֵל הָאָרֶץ, \\
יִשְׂמְחוּ אִים רַבִּים. \\
עָנָן וַעֲרָפֶל סְבִיבָיו \\
צֶדֶק וּמִשְׁפָּט מְכוֹן כִּסְאוֹ. \\
אֹהֲבֵי יְיָ שִׂנְאוּ רָע, \\
שֹׁמֵר נַפְשׁוֹת חֲסִידָיו \\
מִיַּד רְשָׁעִים יַצִילֵם. \\
אוֹר זָרֵעַ לַצַדִּיק \\
וּלְיִשְׁרֵי־לֵב שִׂמְחָה. \\
שִׂמְחוּ צַדִּיקִים בַּיץ \\
וְהוֹדוּ לְזֵכֶר קָדְשׁוֹ.
  \end{hebrew}%
}

\newcommand{\blockC}{%
  PSALM 97:1-2, 10-12 \\
ADONAI malach tageil haaretz, \\
yism'chu iyim rabim. \\
Anan vaarafel s'vivav \\
tzedek umishpat m'chon kiso. \\
Ohavei Adonai sinu ra, \\
shomeir nafshot chasidav \\
miyad r’sha-im yatzileim. \\
Or zarua latzaddik \\
ul'yishrei lev simchah. \\
Simchu tzaddikim b'Adonai \\
v'hodu l'zeicher kodsho.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}