% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 133
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 133.a, 133.b, etc.
\renewcommand{\thepage}{133.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  ADONAI IS SOVEREIGN! \\
Let the earth exult, the many islands rejoice! \\
Dense clouds are around God, \\
righteousness and justice are the base of God's throne. \\
O you who love Adonai, hate evil! \\
God guards the lives of God's loyal ones, \\
saving them from the hand of the wicked. \\
Light is sown for the righteous, \\
radiance for the upright. \\
O you righteous, rejoice in Adonai \\
and acclaim God's holy name!%
}

\newcommand{\blockB}{%
  \begin{hebrew}
  מזְמוֹר. \\
שִׁירוּ לַייָ שִׁיר חָדָשׁ, \\
כִּי־נִפְלָאוֹת עָשָׂה, \\
הוֹשִׁיעָה לוֹ יְמִינוֹ וּזְרוֹעַ קָדְשׁוֹ. \\
הוֹדִיעַ יְיָ יְשׁוּעָתוֹ, \\
T: \\
לְעֵינֵי הַגּוֹיִם גְלָּה צִדְקָתוֹ. \\
זָכַר חַסְדּוֹ וֶאֱמוּנָתוֹ \\
לְבֵית יִשְׂרָאֵל, רָאוּ כָל־אַפְסֵי אָרֶץ \\
אֵת יְשׁוּעַת אֱלֹהֵינוּ. \\
הָרִיעוּ לַייָ כָּל־הָאָרֶץ \\
ז \\
פִּצְחוּ וְרַנְנוּ וְזַמֵרוּ.
  \end{hebrew}%
}

\newcommand{\blockC}{%
  PSALM 98:1-9 \\
MIZMOR. \\
Shiru l'Adonai shir chadash, \\
ki niflaot asah, \\
hoshiah lo y'mino uz'ro-a kodsho. \\
Hodia Adonai y'shuato, \\
l'einei hagoyim gilah tzidkato. \\
Zachar chasdo ve-emunato \\
I'veit Yisrael, ra-u chol afsei aret \\
et y'shuat Eloheinu. \\
Hariu l'Adonai kol haaretz \\
pitz'chu v'ran'nu v'zameiru.%
}

\newcommand{\blockD}{%
  A PSALM. \\
Sing to Adonai a new song, \\
for God has worked wonders; \\
God's right hand, God's holy arm, \\
has won God victory. \\
Adonai has manifested God's victory, \\
has displayed God's triumph in the sight of the nations. \\
God was mindful of God's steadfast love and faithfulness \\
toward the house of Israel; \\
all the ends of the earth beheld the victory of our God. \\
Raise a shout to Adonai, all the earth, \\
break into joyous songs of praise!%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}