% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 134
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 134.a, 134.b, etc.
\renewcommand{\thepage}{134.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  זַמְּרוּ לַייָ בְּכִנּוֹר, \\
בְּכִנּוֹר וְקוֹל זִמְרָה. \\
בַּחֲצֹצְרוֹת וְקוֹל שׁוֹפָר \\
הָרִיעוּ לִפְנֵי הַמֶּלֶךְ יְיָ. \\
יִרְעַם הַיָּם וּמְלֹאוֹ \\
תֵּבֵל וְיֹשְׁבֵי בָהּ. \\
נְהָרוֹת יִמְחֲאוּ־כָף \\
יַחַד הָרִים יְרַנֵּנוּ. \\
לִפְנֵי־יְיָ כִּי־בָא \\
לִשְׁפּט הָאָרֶץ \\
יִשְׁפּט תֵּבֵל בְּצֶדֶק \\
וְעַמִּים בְּמֵישָׁרִים. \\
T:
  \end{hebrew}%
}

\newcommand{\blockB}{%
  Zamru l'Adonai b'chinor, \\
b'chinor v'kol zimrah. \\
Bachatzotz'rot v'kol shofar \\
hariu lifnei HaMelech Adonai. \\
Yiram hayam um'lo-o \\
teiveil v'yoshvei vah. \\
N'harot yimcha-u chaf \\
yachad harim y'raneinu. \\
Lifnei Adonai ki va \\
lishpot haaretz \\
yishpot teiveil b'tzedek \\
v'amim b'meisharim.%
}

\newcommand{\blockC}{%
  SING PRAISE TO ADONAI with the lyre, \\
with the lyre and melodious song. \\
With trumpets and the blast of the horn \\
raise a shout before Adonai, the ruler. \\
Let the sea and all within it thunder, \\
the world and its inhabitants; \\
let the rivers clap their hands, \\
the mountains sing joyously together \\
at the presence of Adonai, \\
for God is coming to rule the earth; \\
God will rule the world justly, \\
and its peoples with equity.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}