% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 139
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 139.a, 139.b, etc.
\renewcommand{\thepage}{139.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  הִתְעוֹרְרִי, הִתְעוֹרְרִי, \\
כִּי בָא אוֹרֵךְ, קְוּמִי אוֹרִי, \\
עוּרִי עוּרִי, שִׁיר דַבֵּרִי, \\
כְּבוֹד יְיָ עָלַיִךְ נִגְלָה. \\
T
  \end{hebrew}%
}

\newcommand{\blockB}{%
  Hitor'ri, hitor'ri, \\
ki va oreich, kumi ori, \\
uri uri shir dabeiri, \\
K'vod Adonai alayich niglah.%
}

\newcommand{\blockC}{%
  Awake, awake, your light has come! Arise, shine, awake and sing: \\
the Eternal's glory dawns upon you.%
}

\newcommand{\blockD}{%
  \begin{hebrew}
  לֹא תֵבוֹשִׁי וְלֹא תִכָּלְמִי, \\
מַה תִּשְׁתּוֹחֲחִי וּמַה הֶאֱמִי, \\
בָּךְ יֶחֱסוּ עֲנִי עַמִּי, \\
וְנִבְנְתָה עִיר עַל תִּלָּהּ. \\
T
  \end{hebrew}%
}

\newcommand{\blockE}{%
  Lo teivoshi v'lo tikalmi, \\
mah tishtochachi umah tehemi, \\
bach yechesu aniyei ami, \\
v'nivn'tah ir al tilah.%
}

\newcommand{\blockF}{%
  An end to shame and degradation; forget your sorrow; quiet your groans. The \\
afflicted of my people find respite in you, the city renewed upon its ancient ruins.%
}

\newcommand{\blockG}{%
  \begin{hebrew}
  וְהָיוּ לִמְשְׁפָּה שׁאֹסָיִךְ, \\
וְרָחֲקוּ כָּל מְבַלְעָיִךְ, \\
יָשִׂישׂ עָלַיִךְ אֱלֹהָיִךְ, \\
כִּמְשׂוֹשׂ חָתָן עַל כַּלָּה. \\
T T
  \end{hebrew}%
}

\newcommand{\blockH}{%
  V'hayu lim'shisah shosayich, \\
v'rachaku kol m'valayich, \\
yasis alayich Elohayich, \\
kimsos chatan al kalah.%
}

\newcommand{\blockI}{%
  The scavengers are scattered, your devourers have fled; \\
as a bridegroom rejoices in his bride, your God takes joy in you.%
}

\newcommand{\blockJ}{%
  \begin{hebrew}
  יָמִין וּשְׂמֹאל תִּפְרוֹצִי, \\
וְאֶת־יְיָ תַּעֲרִיצִי, \\
על יַד אִישׁ בֶּן פַּרְצִי, \\
וְנִשְׂמְחָה וְנָגִילָה. \\
ז
  \end{hebrew}%
}

\newcommand{\blockK}{%
  Yamin usmol tifrotzi, \\
v'et Adonai taaritzi, \\
al yad ish ben partzi, \\
v'nism'chah v'nagilah.%
}

\newcommand{\blockL}{%
  Your space will be broad, your worship free: await the promised one; \\
we will exult, we will sing for joy!%
}

\newcommand{\blockM}{%
  \begin{hebrew}
  בְּוֹאִי בְשָׁלוֹם עֲטֶרֶת בַּעְלָהּ, \\
גַּם בְּשִׂמְחָה וּבְצָהֲלָה, \\
תּוֹךְ אֱמוּנֵי עַם סְגַלָּה, \\
בּוֹאִי כַלָּה, בּוֹאִי כַלָּה.
  \end{hebrew}%
}

\newcommand{\blockN}{%
  Bo-i v'shalom ateret ba'lah, \\
gam b'simchah uv'tzoholah, \\
toch emunei am s'gulah, \\
bo-i chalah, bo-i chalah.%
}

\newcommand{\blockO}{%
  Enter in peace, O crown of your husband; enter in gladness, enter in joy. \\
Come to the people that keeps its faith. Enter, O bride! Enter, O bride!%
}

\newcommand{\blockP}{%
  בּוֹאִי בְשָׁלוֹם \\
For those who choose: When the congregation reaches the last verse, beginning D \\
Bo-i v'shalom, Enter in peace, all rise and turn toward the entrance of the sanctuary, as if to greet \\
the Presence of Shabbat.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\blockG
\vspace{1em}
% \newpage % Uncomment to break page here

\blockH
\vspace{1em}
% \newpage % Uncomment to break page here

\blockI
\vspace{1em}
% \newpage % Uncomment to break page here

\blockJ
\vspace{1em}
% \newpage % Uncomment to break page here

\blockK
\vspace{1em}
% \newpage % Uncomment to break page here

\blockL
\vspace{1em}
% \newpage % Uncomment to break page here

\blockM
\vspace{1em}
% \newpage % Uncomment to break page here

\blockN
\vspace{1em}
% \newpage % Uncomment to break page here

\blockO
\vspace{1em}
% \newpage % Uncomment to break page here

\blockP
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}