% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 140
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 140.a, 140.b, etc.
\renewcommand{\thepage}{140.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  מזמור שיר \\
לְיוֹם הַשַׁבָּת. \\
טוֹב לְהֹדוֹת לַייָ \\
וּלְזַמֵּר לְשִׁמְךְ עֶלְיוֹן. \\
לְהַגִּיד בַּבֹּקֶר חַסְדֶּךָ, \\
וֶאֱמוּנָתְךָ בַּלֵּילוֹת. \\
עֲלֵי עָשׂוֹר וַעֲלֵי נָבֶל, \\
עֲלֵי הִגָּיוֹן בְּכִנּוֹר. \\
כִּי שִׂמַּחְתַּנִי יְיָ בְּפָעָלֶךְ \\
בְּמַעֲשֵׂי יָדֶיךָ אֲרַנֵּן. \\
מַה־גָּדְלוּ מַעֲשֶׂיךָ, יְיָ \\
מְאֹד עָמְקוּ מַחְשְׁבֹתֶיךָ. \\
אִישׁ בַּעַר לֹא יֵדָע \\
וּכְסִיל לֹא־יָבִין אֶת־זֹאת. \\
צַדִּיק כַּתָּמָר יִפְרָח \\
כְּאֶרֶז בַּלְבָנוֹן יִשְׂגֶה. \\
שְׁתוּלִים בְּבֵית יְיָ, \\
בְּחַצְרוֹת אֱלֹהֵינוּ יַפְרִיחוּ. \\
עוֹד יְנוּבוּן בְּשִׂיבָה, \\
דְּשֵׁנִים וְרַעֲנַנִּים יִהְיוּ. \\
לְהַגִּיד כִּי־יָשָׁר יְיָ, \\
צוּרִי וְלֹא־עַוְלָתָה בּוֹ. \\
TIT
  \end{hebrew}%
}

\newcommand{\blockB}{%
  MIZMOR SHIR \\
I'yom HaShabbat. \\
Tov l'hodot l'Adonai \\
ul'zameir l'shimcha elyon. \\
L'hagid babokeir chasdecha, \\
ve-emunatcha baleilot. \\
Alei asor vaalei navel \\
alei higayon b'chinor. \\
Ki simachtani Adonai b'fo-olecha \\
b'maasei yadecha aranein. \\
Mah gadlu maasecha Adonai, \\
m'od amku machsh'votecha. \\
Ish baar lo yeida \\
uch'sil lo yavin et zot. \\
Tzaddik katamar yifrach \\
k'erez bal'vanon yisgeh. \\
Sh'tulim b'veit Adonai, \\
b'chatzrot Eloheinu yafrichu. \\
Od y'nuvun b'seivah, \\
d'sheinim v'raananim yih'yu. \\
L'hagid ki yashar Adonai, \\
tzuri v'lo avlatah bo. \\
PSALM 92:1-7, 13-16%
}

\newcommand{\blockC}{%
  A PSALM. A SONG for Shabbat. \\
It is good to praise Adonai; to sing hymns to Your name, O Most High, \\
to proclaim Your steadfast love at daybreak, Your faithfulness each night, \\
with a ten-stringed harp, with voice and lyre together. \\
You have gladdened me by Your deeds, Adonai; I shout for joy at Your handiwork. \\
How great are Your works, Adonai, how very subtle Your designs! \\
A brute cannot know, a fool cannot understand this: \\
The righteous bloom like a date-palm; they thrive like a cedar in Lebanon; \\
planted in the house of Adonai, they flourish in the courts of our God. \\
In old age they still produce fruit; they are full of sap and freshness, \\
attesting that Adonai is upright, my Rock, in whom there is no wrong.%
}

\newcommand{\blockD}{%
  Psalm 92 - The psalm sung by the Levites in the ancient Temple (M. Tamid 7:4), taken by the \\
Rabbis to refer to the longed-for future time when every day will be like Shabbat. \\
Mechilta d'Rabbi Yishma-eil, Masechta d'Shabta I%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}