% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 141
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 141.a, 141.b, etc.
\renewcommand{\thepage}{141.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  י מָלָךְ גֵאוּת לָבֵשׁ, \\
לָבֵשׁ יְיָ עז הִתְאַגָּר, \\
אַף־תִּכּוֹן תֵּבֵל בַּל־תְּמוֹט. \\
נָכוֹן כִּסְאֲךָ מֵאָז, \\
מֵעוֹלָם אָתָּה. \\
נָשְׂאוּ נְהָרוֹת, יְיָ, \\
נָשְׂאוּ נְהָרוֹת קוֹלָם, \\
יִשְׂאוּ נְהָרוֹת דָּכְיָם. \\
מִקְלוֹת מַיִם רַבִּים, \\
אַדִּירִים מִשְׁבְּרֵי יָם, \\
אַדִּיר בַּמָּרוֹם יְיָ \\
עֵדֹתֶיךָ נֶאֶמְנוּ מְאֹד, \\
לְבֵיתְךָ נָאֲוָה קְדֶשׁ, \\
י לְאֹרֶךְ יָמִים. \\
T
  \end{hebrew}%
}

\newcommand{\blockB}{%
  PSALM 93:1-5 \\
ADONAI MALACH gei-ut laveish, \\
laveish Adonai oz hitazar, \\
af tikon teiveil bal timot. \\
Nachon kisacha mei-az, \\
mei-olam atah. \\
Nasu n'harot Adonai, \\
nasu n'harot kolam, \\
yisu n'harot dochyam. \\
Mikolot mayim rabim, \\
adirim mishb'rei yam, \\
adir bamarom Adonai. \\
Eidotecha ne-emnu m'od, \\
I'veitcha naavah kodesh, \\
Adonai l'orech yamim.%
}

\newcommand{\blockC}{%
  ADONAI IS SOVEREIGN, \\
God is robed in grandeur; \\
Adonai is robed, \\
God is girded with strength. \\
The world stands firm; \\
it cannot be shaken. \\
Your throne stands firm from of old; \\
from eternity You have existed. \\
The ocean sounds, Adonai, \\
the ocean sounds its thunder, \\
the ocean sounds its pounding. \\
Above the thunder of the mighty waters, \\
more majestic than the breakers of the sea \\
is Adonai, majestic on high. \\
Your decrees are indeed enduring; \\
holiness befits Your house, \\
Adonai, for all times.%
}

\newcommand{\blockD}{%
  Proclaiming the completion of God's work of creation and the establishment of \\
divine sovereignty over all, this psalm serves as a fitting climax to Kabbalat Shabbat. See M. Tamid 7:4%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}