% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 143
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 143.a, 143.b, etc.
\renewcommand{\thepage}{143.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  וַיֵּצֵא יַעֲקֹב מִבְּאֵר שָׁבַע וַיֵּלֶךְ \\
חָרָנָה: וַיִּפְגַע בַּמָּקוֹם וַיָּלֶן שָׁם \\
כִּי־בָא הַשֶׁמֶשׁ וַיְקַח מֵאַבְנֵי \\
הַמָּקוֹם וַיָּשֶׂם מְרַאֲשֹׁתָיו \\
וַיִּשְׁכַּב בַּמָּקוֹם הַהוּא: \\
TAT \\
וַיַּחֲלֹם וְהִנֵּה סֶלָם מֵאָב אַרְצָה \\
וְרֹאשׁוֹ מַגִּיעַ הַשָּׁמָיְמָה וְהִנֵּה \\
מַלְאֲכֵי אֱלֹהִים עֹלִים וְיֹרְדִים בּוֹ: \\
וְהִנֵּה יְיָ נִאָב עָלָיו וַיֹּאמַר אֲנִי \\
יְיָ אֱלֹהֵי אַבְרָהָם אָבִיךָ וֵאלֹהֵי \\
יִצְחָק הָאָרֶץ אֲשֶׁר אַתָּה שֹׁכֵב \\
עָלֶיהָ לְךָ אֶתְּנֶנָּה וּלְזַרְעֶךָ: \\
וְהָיָה זַרְעֲךָ כַּעֲפַר הָאָרֶץ \\
וּפָרַצְתָּ יָמָּה וָקֵדְמָה וְצָפְנָה \\
וְנֶגְבָּה וְנִבְרְכוּ בְךָ כָּל־מִשְׁפְּחֹת \\
T \\
הָאֲדָמָה וּבְזַרְעֶךָ: \\
IT \\
IT \\
וְהִנֵּה אָנֹכִי עִמָּךְ וּשְׁמַרְתִּיךָ בְּכָל \\
אֲשֶׁר תֵּלֵךְ וַהֲשִׁבֹתִיךָ אֶל־הָאֲדָמָה \\
הַזֹּאת כִּי לֹא אֶעֶזָבְךָ עַד אֲשֶׁר \\
אִם־עָשִׂיתִי אֵת אֲשֶׁר דִּבַּרְתִּי לָךְ: \\
וַיִּיקַץ יַעֲקֹב מִשְׁנָתוֹ וַיֹּאמַר \\
אָכֵן יֵשׁ יְיָ בַּמָּקוֹם הַזֶּה וְאָנֹכִי \\
לֹא יָדָעְתִּי: \\
זז! \\
וַיִירָא וַיֹּאמַר מַה־נּוֹרָא הַמָּקוֹם \\
הַזֶּה אֵין זֶה כִּי אִם־בֵּית \\
אֱלֹהִים וְזֶה שַׁעַר הַשָּׁמָיִם:
  \end{hebrew}%
}

\newcommand{\blockB}{%
  AND JACOB LEFT Beersheba and set \\
out for Haran. Coming upon a \\
[certain] place, he passed the night \\
there, for the sun was setting; taking \\
one of the stones of the place, he made \\
it his head-rest as he lay down in that \\
place. He dreamed, and lo― a ladder \\
was set on the ground, with its top \\
reaching to heaven, and lo― angels \\
of God going up and coming down \\
on it. And lo - Adonai stood up above \\
it, and said, "I, Adonai, am the God of \\
your father Abraham and God of Isaac: \\
the land on which you are lying I will \\
give to you and to your descendants. \\
And your descendants shall be like the \\
dust of the earth, and you shall spread \\
out to the west and the east and the \\
north and the south. Through you and \\
your descendants all the families of the \\
earth shall find blessing. And here I \\
am, with you: I will watch over you \\
wherever you go, and I will bring you \\
back to this soil. I will not let go of you \\
as long as I have yet to do what I have \\
promised you." \\
Waking from his sleep, Jacob said, \\
"Truly, Adonai is in this place, and I did \\
not know it!" He was awestruck, and \\
said, "How awe-inspiring is this place! \\
This is none other than the house of \\
God, and this is the gate of heaven!"%
}

\newcommand{\blockC}{%
  And so we understand that ordinary people are messengers of the Most High. They go about their \\
tasks in holy anonymity, often, even unknown to themselves. Yet, if they had not been there, if \\
they had not said what they said or did what they did, it would not be the way it is now. We \\
would not be the way we are now. Never forget that you, too, yourself may be a messenger. \\
Perhaps even one whose errand extends over several lifetimes. Lawrence Kushner \\
And Jacob left Beersheba... Genesis 28:10-17%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}