% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 144
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 144.a, 144.b, etc.
\renewcommand{\thepage}{144.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  יִתְגַּדַּל וְיִתְקַדַּשׁ שְׁמֵהּ רַבָּא \\
בְּעָלְמָא דִי בְרָא כִרְעוּתֵהּ, \\
וְיַמְלִיךְ מַלְכוּתֵהּ \\
בְּחַיֵּיכוֹן וּבְיוֹמֵיכוֹן \\
וּבְחַיֵּי דְכָל בֵּית יִשְׂרָאֵל, \\
בַּעֲגָלָא וּבִזְמַן קָרִיב, \\
וְאִמְרוּ: אָמֵן. \\
יְהֵא שְׁמֵהּ רַבָּא מְבָרַךְ \\
לְעָלַם וּלְעָלְמֵי עָלְמַיָּא. \\
יִתְבָּרַךְ וְיִשְׁתַּבַּח וְיִתְפָּאַר \\
וְיִתְרוֹמַם וְיִתְנַשֵׂא, \\
וְיִתְהַדָּר וְיִתְעַלֶּה וְיִתְהַלֵּל \\
שְׁמֵהּ דְּקָדְשָׁא בְּרִיךְ הוּא, \\
לְעֵלָא מִן כָּל בִּרְכָתָא וְשִׁירָתָא, \\
תִּשְׁבְּחָתָא וְנֶחֱמָתָא, \\
דַּאֲמִירָן בְּעָלְמָא, וְאִמְרוּ: אָמֵן.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  YITGADAL v'yitkadash sh’meih raba \\
b'alma di vra chiruteih, \\
v'yamlich malchuteih \\
b'chayeichon \\
uv'yomeichon \\
uv'chayei d'chol beit Yisrael, \\
baagala uvizman kariv, \\
v'imru: Amen. \\
Y'hei sh'meih raba m'varach \\
l'alam ul'almei almaya. \\
Yitbarach v'yishtabach v'yitpaar \\
v'yitromam v'yitnasei, \\
v'yit'hadar v'yitaleh v'yit’halal \\
sh'meih d'kudsha b'rich hu, \\
l'eila min kol birchata v'shirata, \\
tushb'chata v'nechemata, \\
daamiran b'alma, v'imru: Amen.%
}

\newcommand{\blockC}{%
  EXALTED and hallowed be God's great name, \\
in the world which God created, according to plan. \\
May God's majesty be revealed in the days of our lifetime \\
and the life of all Israel \\
speedily, imminently. \\
To which we say: Amen. \\
Blessed be God's great name to all eternity. \\
Blessed, praised, honored, exalted, \\
extolled, glorified, adored, and lauded \\
be the name of the Holy Blessed One, \\
beyond all earthly words and songs of blessing, praise, and comfort. \\
To which we say: Amen.%
}

\newcommand{\blockD}{%
  The WTP Kaddish is marked by long strings of synonyms of praise. The rhythmic repetition of \\
these words is meant to aid one in achieving a higher meditational state. Judith Z. Abrams%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}