% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 145
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 145.a, 145.b, etc.
\renewcommand{\thepage}{145.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  למדני, אֱלֹהִי, בָּרֵךְ וְהִתְפַּלֵּל \\
על סוֹד עָלֶה קָמֵל, \\
עַל נְגַהּ פְּרִי בָּשֵׁל, \\
עַל הַחֲרוּת הַזֹּאת: \\
לִרְאוֹת, לָחוּשׁ, לִנְשֹׁם, \\
לָדַעַת, לְיַחֵל, לְהִכָּשֵׁל. \\
לַמֵּד אֶת שִׂפְתוֹתַי \\
בְּרָכָה וְשִׁיר הַלֵּל, \\
בְּהִתְחַדֵּשׁ זְמַנְךְ \\
עם בְּקֶר וְעִם לֵיל, \\
לְבַל יִהְיֶה יוֹמִי הַיּוֹם \\
כִּתְמוֹל שִׁלְשׁוֹם, \\
לְבַל יִהְיֶה עָלַי יּוֹמִי הֶרְגֵל.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  LAMDEINI, Elohai, bareich v’hitpaleil \\
al sod aleh kameil, \\
al nogah p'ri basheil, \\
al hacheirut hazot; \\
Lirot, lachush, linshom, \\
ladaat, layacheil, l'hikasheil. \\
Lameid et siftotai \\
b'rachah v'shir hallel, \\
b'hit'chadeish z'mancha \\
im boker v'im leil, \\
I'val yih'yeh yomi hayom \\
kitmol shilshom, \\
I'val yih'yeh alai yomi hergeil.%
}

\newcommand{\blockC}{%
  TEACH ME, O God, a blessing, a prayer \\
on the mystery of a withered leaf, \\
on ripened fruit so fair, \\
on the freedom to see, to sense, \\
to breathe, to know, to hope, to despair. \\
Teach my lips a blessing, a hymn of praise, \\
as each morning and night \\
You renew Your days, \\
lest my day be today as the one before; \\
lest routine set my ways.%
}

\newcommand{\blockD}{%
  ENTRANCES to holiness are everywhere. \\
The possibility of ascent is all the time, \\
even at unlikely times and through unlikely places. \\
There is no place on earth without the Presence.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}