% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 147
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 147.a, 147.b, etc.
\renewcommand{\thepage}{147.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  THERE IS ONE who sings the song of his own life, \\
finding everything within himself. \\
There is one who leaves the circle of her self, \\
and sings the song of her people. \\
There is one whose voice rings with the song of humanity, \\
hoping for the highest perfection. \\
And there is one who rises even higher, \\
uniting with all creatures, with all worlds, \\
filling the universe with \\
song. \\
N'vareich! \\
נְבָרֵךְ! \\
Let us bless!%
}

\newcommand{\blockB}{%
  O GOD, You are as near as \\
the very air we breathe, \\
yet \\
farther than the farthermost star. \\
We yearn to reach You. \\
We seek the light and warmth of Your Presence. \\
Though we say You are near, \\
we are lonely and alone. \\
O let our desire be so strong \\
that it will tear the veil that keeps You from our sight! \\
Let Your light release our darkness \\
and reveal the glory and joy of Your Presence.%
}

\newcommand{\blockC}{%
  What does it mean to be called to worship? All serious activity requires preparation. The \\
and blessings that precede 17, Bar'chu are warm-ups for the individual. Now communal \\
begins. The leader asks, “Are you ready to pray?" And we respond, "Yes! Let us pray!" \\
prayers \\
prayer \\
adapted from Richard Levy%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}