% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 149
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 149.a, 149.b, etc.
\renewcommand{\thepage}{149.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  PRAISE to You, Adonai our God, \\
from whom the evening flows. \\
Your wisdom sets the way on which time and season glide; \\
Your breath guides the sail of the stars. \\
Creator of the tide of time and light, \\
You guide the current of day into night. \\
As heaven spans to infinity, \\
You set its course for eternity. \\
Praise to You, Adonai our God, \\
from whom the evening flows. \\
בָּרוּךְ אַתָּה, יְיָ, הַמַּעֲרִיב עֲרָבִים. \\
Baruch atah, Adonai, hamaariv aravim.%
}

\newcommand{\blockB}{%
  THIS IS AN HOUR of change. \\
Within it we stand uncertain on the border of light. \\
Shall we draw back or cross over? \\
Where shall our hearts turn? \\
Shall we draw back, my brother, my sister, \\
or cross over? \\
This is the hour of change, and within it, \\
we stand quietly \\
on the border of light. \\
What lies before us? \\
Shall we draw back, my brother, my sister, \\
or cross over? \\
בָּרוּךְ אַתָּה, יְיָ, הַמַּעֲרִיב עֲרָבִים. \\
Baruch atah, Adonai, hamaariv aravim.%
}

\newcommand{\blockC}{%
  I know that the tide is not an independent force, but merely the submission of the water to the \\
movement of the moon in its orbit. And this orbit in its turn is subject to other orbits which are \\
mightier far than it. And so the whole universe is held fast in the clinging grip of strong hands, \\
the forces of Earth and Sun, planets, and comets, and galaxies, blindly erupting forces ceaselessly \\
stirring in ripples of silence to the very depth of black space. Amos Oz%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}