% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 151
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 151.a, 151.b, etc.
\renewcommand{\thepage}{151.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  AS YOU TAUGHT TORAH \\
to those whose names I bear, \\
teach me Torah, too. \\
Its mystery beckons, \\
yet I struggle with its truth. \\
You meant Torah for me: \\
did You mean the struggle for me, too? \\
Don't let me struggle alone; \\
help me \\
to understand, \\
to be wise, to listen, to know... \\
Lead me into the mystery. \\
בָּרוּךְ אַתָּה, יְיָ, אוֹהֵב עַמּוֹ יִשְׂרָאֵל. \\
Baruch atah, Adonai, ohev amo Yisrael.%
}

\newcommand{\blockB}{%
  WISDOM AND WONDER, \\
passion and instruction, \\
story and symbol. \\
All these things, \\
Your Torah gives to us. \\
And the more we devote ourselves to it, \\
the more it grows and gives. \\
What could be a truer token \\
of Your abiding love \\
than this holiest of Your works, \\
and the living language \\
that gives it form? \\
בָּרוּךְ אַתָּה, יְיָ, אוֹהֵב עַמּוֹ יִשְׂרָאֵל. \\
Baruch atah, Adonai, ohev amo Yisrael.%
}

\newcommand{\blockC}{%
  Torah is what God has revealed to us, and what we discern of God: ideas and ideals, laws and \\
mitzvot, our religious heritage. It unfolds our memories of Abraham and Sarah, of Moses and \\
Miriam and the Prophets. It is legislation and explanation, allowing questions that challenge, \\
answers that inspire: all a quest for meaning. It is our way of life, a path for our souls, and the \\
design for a better world. John Rayner%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}