% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 155
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 155.a, 155.b, etc.
\renewcommand{\thepage}{155.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  LOVE your God with every heartbeat, \\
with every breath, \\
with every conscious act. \\
Keep in mind the words I command you today. \\
Teach them to your children, \\
talk about them at work: \\
whether you are tired or you are rested. \\
Let them guide the work of your hands; \\
keep them in the forefront of your vision. \\
Do not leave them at the doorway of your house, \\
or outside your gate. \\
They are reminders to do all of My mitzvot, \\
so that you can be holy for God. \\
I am Adonai your God. \\
I led you out of Egypt to become your God, \\
I am Adonai your God!%
}

\newcommand{\blockB}{%
  Judaism is a doing which can be grasped only by the heart. Julius Lester \\
When people come to you for help, do not turn them off with pious words, saying: “Have faith \\
and take your troubles to God!" Act instead as if there were no God, as though there were only \\
one person in all the world who could help - only yourself. Martin Buber \\
Abaye said: Spread the love of God through your actions. If you yourself study and help others \\
to do so, if your business activities are decent and trustworthy, what will people say? “Have you \\
seen the behavior of one who studies Torah? How beautiful! What a fine person!" Thus Isaiah \\
(49:3) taught, "You are My servant Israel. I will be glorified through you." based on Yoma 86a%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}