% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 157
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 157.a, 157.b, etc.
\renewcommand{\thepage}{157.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  STANDING on the parted shores of history \\
we still believe what we were taught \\
before ever we stood at Sinai's foot; \\
that wherever we go, it is eternally Egypt \\
that there is a better place, a promised land; \\
that the winding way to that promise \\
passes through the wilderness. \\
That there is no way to get from here to there \\
except by joining hands, marching \\
together.%
}

\newcommand{\blockB}{%
  IN A WORLD torn by violence and pain, \\
a world far from wholeness and peace, \\
Adonai: \\
give us the courage to say, \\
There is one God in heaven and earth. \\
The high heavens declare Your glory; \\
may earth reveal Your justice and love. \\
From bondage in Egypt, we were delivered; \\
at Sinai, we bound ourselves to Your way. \\
Inspired by prophets and instructed by sages, \\
time and again, we overcame oppressive forces. \\
Though our failings are many and our faults are great, \\
it has been our glory to bear witness to our God, \\
keeping alive in dark ages \\
Your vision of a world redeemed. \\
Let us continue to work for the day \\
when the nations will be one and at peace. \\
Then shall we rejoice as Israel did, \\
singing on the shores of the Sea:%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}