% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 161
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 161.a, 161.b, etc.
\renewcommand{\thepage}{161.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  LET THERE BE love and understanding among us. \\
and friendship be our shelter from life's storms. \\
Let peace \\
Adonai, help us to walk with good companions, \\
to live with hope in our hearts and eternity in our thoughts, \\
that we may lie down in peace and rise up waiting to do Your will. \\
בָּרוּךְ אַתָּה, יְיָ, הַפּוֹרֵשׂ סֶכַּת שָׁלוֹם עָלֵינוּ \\
וְעַל כָּל עַמּוֹ יִשְׂרָאֵל וְעַל יְרוּשָׁלָיִם. \\
Baruch atah, Adonai, haporeis sukat shalom aleinu \\
v'al kol amo Yisrael v'al Yerushalayim.%
}

\newcommand{\blockB}{%
  GIVE US A PLACE TO REST, Adonai, our God. \\
Bring us into shelter \\
in the soft, long, evening shadows of Your truth. \\
For with You are true protection and safety, \\
and in Your Presence are acceptance and gentle love. \\
Watch over us as we go forth. \\
Prepare for us as we return. \\
Spread over us Your shelter of peace, \\
over all we love - over our Jerusalem and Yours. \\
בָּרוּךְ אַתָּה, יְיָ, הַפּוֹרֵשׂ סֶכַּת שָׁלוֹם עָלֵינוּ \\
וְעַל כָּל עַמּוֹ יִשְׂרָאֵל וְעַל יְרוּשָׁלָיִם. \\
Baruch atah, Adonai, haporeis sukat shalom aleinu \\
v'al kol amo Yisrael v'al Yerushalayim.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}