% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 162
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 162.a, 162.b, etc.
\renewcommand{\thepage}{162.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  וְשָׁמְרוּ בְנֵי יִשְׂרָאֵל \\
אֶת־הַשַּׁבָּת, \\
לַעֲשׂוֹת אֶת־הַשַׁבָּת לְדֹרֹתָם \\
בְּרִית עוֹלָם. \\
בֵּינִי וּבֵין בְּנֵי יִשְׂרָאֵל \\
אוֹת הִיא לְעלָם, \\
TH \\
כִּי־שֵׁשֶׁת יָמִים עָשָׂה יְיָ \\
אֶת־הַשָּׁמַיִם וְאֶת־הָאָרֶץ, \\
וּבַיּוֹם הַשְּׁבִיעִי שָׁבַת וַיִּנָּפַשׁ.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  V'SHAMRU V'NEI YISRAEL \\
et HaShabbat, \\
laasot et HaShabbat I'dorotam \\
b'rit olam. \\
Beini u'vein b’nei Yisrael \\
ot hi l'olam, \\
ki sheishet yamim asah Adonai \\
et hashamayim v'et haaretz, \\
u'vayom hashvi-i shavat vayinafash.%
}

\newcommand{\blockC}{%
  THE PEOPLE OF ISRAEL shall keep Shabbat, \\
observing Shabbat throughout the ages as a covenant for all time. \\
It is a sign for all time between Me and the people of Israel. \\
For in six days Adonai made heaven and earth, \\
and on the seventh day God ceased from work and was refreshed.%
}

\newcommand{\blockD}{%
  \begin{hebrew}
  ישְׂמָחוּ בְמַלְכוּתְךָ \\
שׁוֹמְרֵי שַׁבָּת וְקְוֹרְאֵי עֹנֶג. \\
עַם מְקַדְּשֵׁי שְׁבִיעִי, \\
כֻּלָּם יִשְׂבְּעוּ וְיִתְעַנְגוּ מְטוּבָךְ. \\
וְהַשְׁבִיעִי רָצִיתָ בּוֹ וְקִדַּשְׁתּוֹ, \\
חֶמְדַת יָמִים אוֹתוֹ קָרָאתָ, \\
זֵכֶר לְמַעֲשֵׂה בְרֵאשִׁית.
  \end{hebrew}%
}

\newcommand{\blockE}{%
  YISM'CHU v'malchut'cha \\
shomrei Shabbat v'korei oneg. \\
Am m'kad'shei shvi-i, \\
kulam yisb'u v'yitangu mituvecha. \\
V'hashvi-i ratzita bo v'kidashto, \\
chemdat yamim oto karata, \\
zeicher l'maaseh v'reishit.%
}

\newcommand{\blockF}{%
  THOSE WHO KEEP SHABBAT by calling it a delight \\
will rejoice in Your realm. \\
The people that hallow Shabbat will delight in Your goodness. \\
For, being pleased with the Seventh Day, You hallowed it \\
as the most precious of days, drawing our attention to the work of Creation.%
}

\newcommand{\blockG}{%
  V'shamru v'nei Yisrael... The people of Israel shall keep... Exodus 31:16-17 \\
Yism'chu contains twenty-four Hebrew words said to correspond to the twenty-four hours of Shabbat.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\blockG
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}