% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 167
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 167.a, 167.b, etc.
\renewcommand{\thepage}{167.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  SOME PERISHED by fire, some by water. \\
Some crossed the sea, or watered the desert. \\
Some starved all week to make a Shabbat feast. \\
Some were left childless until old age. \\
Some lifted their chins beneath a father's knife. \\
Those who came before us gave everything \\
so that we, generations later, could glorify You. \\
And despite the dangers, with Your protection, \\
some did survive, and even flourished, \\
some reaped in joy, were spared the knife, \\
were granted children. \\
We are their inheritors, O God, \\
and we know how rare is our good fortune \\
to be born to such hard-won treasures. \\
A great responsibility is ours, \\
and Yours as well, \\
for if You do not sustain us, \\
as you did Abraham and Sarah, \\
Rebecca and Isaac, Jacob, Rachel and Leah, \\
then who will sing Your praises? \\
Who will lift their chins, as we do now, \\
to sanctify Your name? \\
בָּרוּךְ אַתָּה, יְיָ, פּוֹקֵד שָׂרָה וּמָגֵן אַבְרָהָם. \\
Baruch atah, Adonai, pokeid Sarah u'magein Avraham.%
}

\newcommand{\blockB}{%
  ... The word of Adonai came to Abram in a vision, saying: 'Fear not, Abram, I am a shield to \\
you and your reward shall be very great . . . Look to the heaven and count the stars. . . So shall \\
your offspring be.' And because he put his trust in God, God reckoned it to his merit." \\
Genesis 15:1, 5, 6 \\
In difficult moments of our lives we turn to God to help and sustain us. The classic chatimah \\
(conclusion) to the Avot/Imahot prayer evokes God as "Abraham's shield." In this egalitarian \\
version we evoke Genesis 21:1 where God takes note of Sarah (TP pokeid) as she struggles with \\
infertility. The chatimah, as with the rest of the prayer, indicates that each of us experiences God \\
differently.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}