% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 168
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 168.a, 168.b, etc.
\renewcommand{\thepage}{168.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  אַתָּה גִּבּוֹר לְעוֹלָם, אֲדֹנָי, \\
מְחַיֶה הַכֹּל מֵתִים) אַתָּה, \\
רַב לְהוֹשִׁיעַ. \\
*WINTER – מַשִׁיב הָרוּחַ \\
וּמוֹרִיד הַגָּשֶׁם. \\
*SUMMER - מוֹרִיד הַטָּל. \\
מְכַלְכֵּל חַיִּים בְּחֶסֶד, \\
מְחַיֶה הַכֹּל מִתִים) \\
בְּרַחֲמִים רַבִּים, סוֹמֵךְ נוֹפְלִים, \\
וְרוֹפֵא חוֹלִים, וּמַתִּיר אֲסוּרִים, \\
וּמְקַיִם אֱמוּנָתוֹ לִישֵׁנִי עָפָר. \\
מִי כָמְוֹךְ בַּעַל גְבוּרוֹת \\
1 \\
וּמִי דְוֹמֶה לָךְ, מֶלֶךְ מֵמִית \\
וּמְחַיֶה וּמַצְמִיחַ יְשׁוּעָה. \\
SHABBAT SHUVAH \\
מִי כָמוֹךְ אַב הָרַחֲמִים, \\
זוֹכֵר יְצוּרָיו לְחַיִּים בְּרַחֲמִים. \\
וְנֶאֱמָן אַתָּה לְהַחֲיוֹת הַכֹּל מֵתִים). \\
בָּרוּךְ אַתָּה, יְיָ, מְחַיֶה הַכֹּל וְהַמֶּתִים). \\
:
  \end{hebrew}%
}

\newcommand{\blockB}{%
  ATAH gibor l'olam, Adonai, \\
m'chayeih hakol (meitim) atah, \\
rav l'hoshia. \\
*WINTER — Mashiv haruach \\
umorid hagashem. \\
*SUMMER — Morid hatal. \\
M'chalkeil chayim b'chesed, \\
m'chayeih hakol (meitim) \\
b'rachamim rabim, someich noflim, \\
v'rofei cholim, umatir asurim, \\
um'kayeim emunato lisheinei afar. \\
Mi chamochah baal g'vurot \\
umi domeh lach, melech meimit \\
um'chayeh umatzmiach y'shuah. \\
SHABBAT SHUVAH · \\
Mi chamochah Av harachamim, \\
zocheir y'tzurav l'chayim b'rachamim. \\
V'ne-eman atah l'hachayot hakol (meitim). \\
Baruch atah, Adonai, m'chayeih hakol (hameitim).%
}

\newcommand{\blockC}{%
  YOU ARE FOREVER MIGHTY, Adonai; You give life to all (revive the dead). \\
WINTER - You cause the wind to shift and rain to fall. \\
SUMMER You rain dew upon us. \\
- \\
You sustain life through love, giving life to all (reviving the dead) through great \\
compassion, supporting the fallen, healing the sick, freeing the captive, keeping faith \\
with those who sleep in the dust. Who is like You, Source of mighty acts? Who \\
resembles You, a Sovereign who takes and gives life, causing deliverance to spring up \\
and faithfully giving life to all (reviving that which is dead)? \\
SHABBAT SHUVAH-Who is like You, Compassionate God, \\
who mercifully remembers Your creatures for life? \\
Blessed are You, Adonai, who gives life to all (who revives the dead). \\
בָּרוּךְ אַתָּה, יְיָ, מְחַיֶה הַכֹּל (הַמֶּתִים). \\
Baruch atah, Adonai, m'chayeih hakol (hameitim).%
}

\newcommand{\blockD}{%
  An Mashiv haruach / Morid hatal—with these words, we join our Israeli \\
brothers and sisters in their prayers for seasonal rains in the Land of Israel. \\
Sun in Morid hatal... You rain dew upon us... A seasonal insertion into the Gvurot \\
acknowledges God as the Source of the power of nature. The variations in climate like growth and decay, \\
birth and death, are part of the fixed pattern of the universe created by God. In his prayerbook, Minhag \\
America, Isaac Mayer Wise used the prayer for dew and rain as a permanent part of this benediction. \\
*WINTER: Shmini Atzeret / Simchat Torah to Pesach. \\
SUMMER: Pesach to Shmini Atzeret / Simchat Torah.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}