% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 169
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 169.a, 169.b, etc.
\renewcommand{\thepage}{169.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  WE PRAY that we might know before whom we stand: \\
the Power whose gift is life, \\
who quickens those who have forgotten how to live. \\
We \\
pray \\
for the winds to disperse the choking air of sadness, \\
for cleansing rains to make parched hopes flower, \\
and to give all of us the strength to rise up toward the sun. \\
We pray for love to encompass us \\
for no other reason save that we are human, \\
for love through which we may all blossom into persons \\
who have gained power over our own lives. \\
We \\
pray to stand upright, we fallen; \\
to be healed, we sufferers; \\
we pray to break the bonds that keep us from the world of beauty; \\
we pray for opened eyes, \\
we who are blind to our own authentic selves. \\
We pray that we may walk in the garden of a purposeful life, \\
our own powers in touch with the power of the world. \\
Praised be the God whose gift is life, \\
whose cleansing rains let parched men and women \\
flower toward the sun. \\
בָּרוּךְ אַתָּה, יְיָ, מְחַיֶה הַכֹּל וְהַמֶּתִים). \\
Baruch atah, Adonai, m'chayeih hakol (hameitim).%
}

\newcommand{\blockB}{%
  The metaphor "reviving the dead" is widely used rabbinically. The Talmud recommends saying \\
Baruch atah Adonai, mchayeih hameitim for greeting a friend after a lapse of seeing the person for twelve months, and for awakening from sleep. \\
B'rachot 58b, Y. B'rachot 4:2%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}