% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 171
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 171.a, 171.b, etc.
\renewcommand{\thepage}{171.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  DAYS PASS and the years vanish, and we walk sightless among miracles. \\
God, fill our eyes with seeing and our minds with knowing; \\
let there be moments when Your Presence, like lightning, \\
illumines the darkness in which we walk. \\
Help us to see, wherever we gaze, that the bush burns unconsumed. \\
And we, clay touched by God, will reach out for holiness, and exclaim in wonder: \\
How filled with awe is this place, and we did not know it! \\
Blessed is the Eternal One, the Holy God! \\
בָּרוּךְ אַתָּה, יְיָ, הָאֵל הַקָּדוֹשׁ. \\
Baruch atah, Adonai, Ha-El hakadosh.%
}

\newcommand{\blockB}{%
  \begin{hebrew}
  יָהּ אָנָה אֶמְצָאֲךָ \\
מְקוֹמְךָ נַעֲלָה וְנֶעְלָם \\
וְאָנָה לֹא אֶמְצָאֲךָ \\
כְּבוֹדְךָ מָלֵא עוֹלָם. \\
TIT \\
דָּרַשְׁתִּי קִרְבָתְךָ \\
בְּכָל לִבִּי קְרָאתִיךָ \\
וּבְצֵאתִי לִקְרָאתְךָ \\
לִקְרָאתִי מְצָאתִיךָ.
  \end{hebrew}%
}

\newcommand{\blockC}{%
  WHERE might I go to find You, \\
Exalted, Hidden One? \\
Yet where would I not go to find You, \\
Everpresent, Eternal One? \\
My heart cries out to You: \\
Please draw near to me. \\
The moment I reach out for You, \\
I find You reaching in for me.%
}

\newcommand{\blockD}{%
  \begin{hebrew}
  בָּרוּךְ אַתָּה, יְיָ, הָאֵל הַקָּדוֹשׁ. \\
Baruch atah, Adonai, Ha-El hakadosh.
  \end{hebrew}%
}

\newcommand{\blockE}{%
  Holiness occurs when power and goodness co-exist in perfect harmony. \\
adapted from Mordecai Kaplan \\
How shall we sanctify God's name? By being holy ourselves. How do we accomplish this? Let our \\
prayers bring us to sacred deed, to actions that promote justice, harmony and peace.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}