% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 173
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 173.a, 173.b, etc.
\renewcommand{\thepage}{173.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  MAY THESE HOURS of rest and renewal \\
open our hearts to joy and our minds to truth. \\
May all who struggle find rest on this day. \\
May all who suffer find solace. \\
May all who hurt find healing on this day. \\
May all who despair find purpose. \\
May all who hunger find fulfillment on this day. \\
And may this day fulfill its promise. \\
בָּרוּךְ אַתָּה, יְיָ, מְקַדֵּשׁ הַשַׁבָּת. \\
Baruch atah, Adonai, m'kadeish HaShabbat.%
}

\newcommand{\blockB}{%
  DISTURB US, Adonai, ruffle us from our complacency; \\
Make us dissatisfied. Dissatisfied with the peace of ignorance, \\
the quietude which arises from a shunning of the horror, the defeat, \\
the bitterness and the poverty, physical and spiritual, of humans. \\
Shock us, Adonai, deny to us the false Shabbat which gives us \\
the delusions of satisfaction amid a world of war and hatred; \\
Wake us, O God, and shake us \\
from the sweet and sad poignancies rendered by \\
half forgotten melodies and rubric prayers of yesteryears; \\
Make us know that the border of the sanctuary \\
is not the border of living \\
and the walls of Your temples are not shelters \\
from the winds of truth, justice and reality. \\
Disturb us, O God, and vex us; \\
let not Your Shabbat be a day of torpor and slumber; \\
let it be a time to be stirred and spurred to action. \\
בָּרוּךְ אַתָּה, יְיָ, מְקַדֶשׁ הַשַׁבָּת. \\
Baruch atah, Adonai, m'kadeish HaShabbat.%
}

\newcommand{\blockC}{%
  The meaning of Shabbat is to celebrate time rather than space. Six days a week we live under the \\
tyranny of things in space; on Shabbat we try to become attuned to the holiness of time. It is a \\
day on which we are called upon to share in what is eternal in time, to turn from the results of \\
Creation to the mystery of Creation, from the world of Creation to the creation of the world. \\
Abraham Joshua Heschel%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}