% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 175
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 175.a, 175.b, etc.
\renewcommand{\thepage}{175.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  רְצָה, יְיָ אֱלֹהֵינוּ, בְּעַמָּךְ יִשְׂרָאֵל, \\
וּתְפִלָּתָם בְּאַהֲבָה תְקַבֵּל, \\
וּתְהִי לְרָצוֹן תָּמִיד \\
עֲבוֹדַת יִשְׂרָאֵל עַמֶּךָ. \\
בָּרוּךְ אַתָּה, יְיָ, \\
שֶׁאוֹתְךָ לְבַדְּךָ בְּיִרְאָה נַעֲבֹד. \\
T
  \end{hebrew}%
}

\newcommand{\blockB}{%
  R'TZEI, Adonai Eloheinu, b'amcha Yisrael, \\
ut'filatam b'ahavah t'kabeil, \\
ut'hi l'ratzon tamid \\
avodat Yisrael amecha. \\
Baruch atah, Adonai, \\
she-ot-cha l'vadcha b'yirah naavod. \\
EVERPRESENT ONE, may we, Your people Israel, \\
be worthy in our deeds and our prayer. \\
Wherever we live, wherever we seek You \\
in this land, in Zion restored, in all lands \\
You are our God, whom alone we serve in reverence. \\
בָּרוּךְ אַתָּה, יְיָ, שֶׁאוֹתְךָ לְבַדְּךָ בְּיִרְאָה נַעֲבֹד. \\
T: \\
Baruch atah, Adonai, she-ot'cha l'vad'cha b'yirah naavod.%
}

\newcommand{\blockC}{%
  YOU ARE WITH US in our prayer, our love and our doubt, \\
in our longing to feel Your Presence and do Your will. \\
You are the still clear voice within us. \\
Therefore, O God, when doubt troubles us, \\
when anxiety makes us tremble, \\
when pain clouds the mind, \\
we look inward for the answer to our prayers. \\
There may we find You, \\
and there find courage, insight and endurance. \\
And let our worship bring us closer to one another, \\
that all Israel, and all who seek You, \\
may find new strength for Your service. \\
בָּרוּךְ אַתָּה, יְיָ, שֶׁאוֹתְךָ לְבַדְּךָ בְּיִרְאָה נַעֲבֹד. \\
Baruch atah, Adonai, she-ot'cha l'vad'cha b'yirah naavod.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}