% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 177
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 177.a, 177.b, etc.
\renewcommand{\thepage}{177.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  GOD OF GOODNESS, we give thanks \\
for the gift of life, wonder beyond words; \\
for the awareness of soul, our light within; \\
for the world around us, so filled with beauty; \\
for the richness of the earth, which day by day sustains us; \\
for all these and more, we offer thanks. \\
בָּרוּךְ אַתָּה, יְיָ, הַטוֹב שִׁמְךְ וּלְךָ נָאֶה לְהוֹדוֹת. \\
Baruch atah, Adonai, hatov shimcha ul'cha na-eh l'hodot.%
}

\newcommand{\blockB}{%
  WHEN WE BEHOLD Your heavens, the work of Your fingers, \\
the moon and stars that You set in place \\
What are we humans that You are mindful of us? \\
We mortals that You take note of us? \\
You made us little less than divine, \\
adorned us with glory and majesty. \\
You gave us dominion over Your handiwork, \\
laying the world at our feet... \\
how majestic is Your name throughout the earth! \\
בָּרוּךְ אַתָּה, יְיָ, הַטוֹב שִׁמְךְ וּלְךָ נָאֶה לְהוֹדוֹת. \\
Baruch atah, Adonai, hatov shimcha ul'cha na-eh l'hodot.%
}

\newcommand{\blockC}{%
  For those who choose: On page 176, at the word in Modim, one bows at the waist. At » \\
Adonai, one stands up straight. \\
When we behold Your heavens... Psalm 8:4-7, 10%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}