% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 179
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 179.a, 179.b, etc.
\renewcommand{\thepage}{179.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  GRANT US PEACE, Your most precious gift, \\
O Eternal Source of peace. \\
And give us the will to proclaim its message \\
to all the peoples of the earth. \\
Bless our country as a safeguard of peace, \\
its advocate among the nations. \\
May contentment reign within our borders, \\
health and happiness within our homes. \\
Strengthen the bonds of friendship and fellowship \\
among all the inhabitants of every land. \\
Plant virtue in every soul, \\
and may the love of Your Name hallow every home and every heart. \\
Praised are You, Eternal One, who blesses our people with peace. \\
בָּרוּךְ אַתָּה, יְיָ הַמְבָרֵךְ אֶת עַמּוֹ יִשְׂרָאֵל בַּשָׁלוֹם. \\
1: \\
Baruch atah, Adonai, ham'vareich et amo Yisrael bashalom.%
}

\newcommand{\blockB}{%
  \begin{hebrew}
  לא־יִשָּׂא גוֹי אֶל גּוֹי חֶרֶב, \\
וְלֹא־יִלְמְדוּ עוֹד מִלְחָמָה.
  \end{hebrew}%
}

\newcommand{\blockC}{%
  LO YISA GOI el goi cherev. \\
V'lo yilm'du od milchamah.%
}

\newcommand{\blockD}{%
  NATION shall not take up sword against nation; they shall never again know war.%
}

\newcommand{\blockE}{%
  DON'T STOP after beating the swords \\
into ploughshares, don't stop! Go on beating \\
and make musical instruments out of them. \\
Whoever wants to make war again \\
will have to turn them into ploughshares first.%
}

\newcommand{\blockF}{%
  Great is peace, for peace is to the world as leaven is to dough. Perek HaShalom 1:1 \\
By three things does the world endure: justice, truth, and peace. R. Muna said: The three are one \\
because if justice is done, truth has been effected and peace is brought about. Perek HaShalom 1:2 \\
Great is peace, for even in a time of war one should begin (by attempting to arrange) peace. \\
Perek HaShalom 1:14 \\
NN Lo yisa goi... Nation shall not... Isaiah 2:4%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}