% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 180
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 180.a, 180.b, etc.
\renewcommand{\thepage}{180.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  אֱלֹהַי, נְצֹר לְשׁוֹנִי מֵרָע וּשְׂפָתַי \\
מִדַּבֵּר מִרְמָה, וְלִמְקַלְלַי נַפְשִׁי \\
תִדּוֹם, וְנַפְשִׁי בֶּעָפָר לַכֹּל תִּהְיֶה. \\
פְּתַח לִבִּי בְּתוֹרָתֶךָ, וּבְמִצְוֹתֶיךָ \\
תִּרְדוֹף נַפְשִׁי, וְכֹל הַחוֹשְׁבִים \\
עָלַי רָעָה, מְהֵרָה הָפַר עֲצָתָם \\
וְקַלְקֵל מַחֲשַׁבְתָּם. עֲשֵׂה לְמַעַן \\
שְׁמֶךָ, עֲשֵׂה לְמַעַן יְמִינֶךָ, עֲשֵׂה \\
לְמַעַן קְדֶשָׁתֶךָ, עֲשֵׂה לְמַעַן \\
תּוֹרָתֶךָ. לְמַעַן יֵחָלְצוּן יְדִידֶיךָ, \\
הוֹשִׁיעָה יְמִינְךָ וַעֲנֵנִי.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  ELOHAI, n'tzor l'shoni meira us'fatai \\
midabeir mirmah, v'limkal'lai nafshi \\
tidom, v'nafshi ke-afar lakol tih'yeh. \\
P'tach libi b'Toratecha, uv'mitzvotecha \\
tirdof nafshi. V'chol hachoshvim \\
alai raah, m'heirah hafeir atzatam \\
v'kalkeil machashavtam. Aseih I'maan \\
sh'mecha, aseih I'maan y'minecha, aseih \\
I'maan k'dushatecha, aseih I'maan \\
Toratecha. L'maan yeichaltzun y'didecha, \\
hoshiah y'mincha vaaneini.%
}

\newcommand{\blockC}{%
  MY GOD, guard my speech from evil and my lips from deception. \\
Before those who slander me, I will hold my tongue; I will practice humility. \\
Open my heart to Your Torah, that I may pursue Your mitzvot. \\
As for all who think evil of me, cancel their designs and frustrate their schemes. \\
Act for Your own sake, for the sake of Your Power, \\
for the sake of Your Holiness, for the sake of Your Torah; \\
so that Your loved ones may be rescued, save with Your power. And answer me.%
}

\newcommand{\blockD}{%
  \begin{hebrew}
  יִהְיוּ לְרָצוֹן אִמְרֵי פִי וְהֶגְיוֹן לִבִּי \\
>> \\
לְפָנֶיךָ, יְיָ צוּרִי וְגוֹאֲלִי.
  \end{hebrew}%
}

\newcommand{\blockE}{%
  Yih'yu l'ratzon imrei fi v'hegyon libi \\
l'fanecha, Adonai tzuri v'go-ali.%
}

\newcommand{\blockF}{%
  May the words of my mouth and the meditations of my heart \\
be acceptable to You, Adonai, my Rock and my Redeemer.%
}

\newcommand{\blockG}{%
  \begin{hebrew}
  עשֶׂה שָׁלוֹם בִּמְרוֹמָיו, \\
הוּא יַעֲשֶׂה שָׁלוֹם עָלֵינוּ \\
וְעַל כָּל יִשְׂרָאֵל, וְעַל כָּל יוֹשְׁבֵי תֵבֵל, \\
וְאִמְרוּ: אָמֵן.
  \end{hebrew}%
}

\newcommand{\blockH}{%
  Oseh shalom bimromav, \\
hu yaaseh shalom aleinu, \\
v'al kol Yisrael, v'al kol yoshvei teiveil, \\
v'imru: Amen.%
}

\newcommand{\blockI}{%
  make \\
May the One who makes peace in the high heavens \\
peace \\
for us, for all Israel and all who inhabit the earth. Amen.%
}

\newcommand{\blockJ}{%
  For those who count the Omer, every evening between Pesach and Shavuot, turn to page 570. \\
Reading of the Torah is on page 362. Aleinu and Kaddish are on pages 586–587.%
}

\newcommand{\blockK}{%
  Elohai, n'tzor l'shoni meira... My God, guard my speech from evil... \\
based on Psalm 34:14 \\
יֵחָלְצוּן \\
ph I'maan yeichaltzun... so that Your loved ones... \\
Psalm 60:7 \\
Yih'yu l'ratzon... May the words of my mouth... Psalm 19:15%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\blockG
\vspace{1em}
% \newpage % Uncomment to break page here

\blockH
\vspace{1em}
% \newpage % Uncomment to break page here

\blockI
\vspace{1em}
% \newpage % Uncomment to break page here

\blockJ
\vspace{1em}
% \newpage % Uncomment to break page here

\blockK
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}