% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 181
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 181.a, 181.b, etc.
\renewcommand{\thepage}{181.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  CREATE a pure heart within me; \\
let my soul wake up in Your light. \\
Open me to Your Presence; \\
flood me with Your holy spirit. \\
Then I will stand and sing out \\
the power of Your forgiveness. \\
I will teach Your love to the lonely; \\
the lost will find their way home. \\
Adonai, open up my lips \\
and my mouth will declare Your praise.%
}

\newcommand{\blockB}{%
  WE REACH for You, our God \\
from our quiet places. \\
May we stand still, for a brief moment, \\
and listen to the rain - \\
Stand still, for a brief moment, \\
and watch the play of sunlight and shadow on the leaves. \\
For a brief moment listen to the world. \\
Let us stop the wheels of every day to be aware of Shabbat. \\
Find the stillness of the sanctuary which the soul cherished. \\
Renew the Covenant of an ancient people. \\
We need a quiet space to test the balance of our days. \\
The weight of our own deeds \\
against the heaviness of the world's demands. \\
The balance is precarious - steady us with faith: \\
Quiet places and stillness - \\
where we will hear our own best impulses speak. \\
Quiet places and stillness \\
from which we will reach out to each other. \\
We will find strength in silence \\
and with this strength \\
we will turn again to Your service.%
}

\newcommand{\blockC}{%
  For those who count the Omer, every evening between Pesach and Shavuot, turn to page 570. \\
Reading of the Torah is on page 362. Aleinu and Kaddish are on pages 586–587. \\
Create a pure heart within me . . . adapted from Psalm 51%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}