% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 183
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 183.a, 183.b, etc.
\renewcommand{\thepage}{183.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  LET US PRAISE Adonai, \\
Source of knowledge and light, \\
from whom we draw wisdom and insight. \\
Let us savor the fullness of each and every day \\
and fill our souls with the treasures of Shabbat. \\
And let us appreciate these distinctions: \\
sacred from profane, charity from greed, \\
purpose from drift. \\
Let us affirm our covenant as God's people. \\
Let us honor those who study Torah. \\
Let us uphold the truth of ongoing revelation. \\
Let us celebrate the glory of our tradition \\
and draw refreshment from the wellsprings of prayer. \\
Let us respect tradition and encourage creative faith. \\
And let us dress ourselves in the garments of God \\
compassion for the needy, embrace of the stranger \\
and then spread the canopy of peace over all the world.%
}

\newcommand{\blockB}{%
  MAGEIN AVOT V'IMAHOT%
}

\newcommand{\blockC}{%
  In this traditional prayer that summarizes the Amidah for Friday night, God appears uniquely as \\
mon hab'rachot, literally, an “abode” (or “place") of blessing. Over time, however, \\
this reading was lost through a scribal error, and does not appear in traditional prayer books. We \\
restore it here, so as to sense God as a place where we can enter and be at home, a spiritual \\
destination where we go to find the blessings we seek.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}