% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 7
% ==========================================
\documentclass[14pt]{extarticle}
\usepackage[paperwidth=5.5in, paperheight=8.5in, margin=0.6in]{geometry}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\setotherlanguage{hebrew}
\newfontfamily\hebrewfont[Script=Hebrew]{Ezra SIL} % Update your local system font here

% Custom page numbering to yield 7.a, 7.b, etc.
\renewcommand{\thepage}{7.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  OUR PRAISE to You, Eternal One, who brings the evening evermore: \\
wisely parting the gates of time, ushering in the seasons; \\
arraying with care the star-spangled sky; \\
unfurling light, then darkness, then light. \\
Gently You fold the day into the night, \\
Adonai Tzvaot is Your Name! \\
Living God, Your reign arches over us, Your light is everlasting. \\
Our praise to You, Eternal One, who brings the evening evermore. \\
בָּרוּךְ אַתָּה, יְיָ, הַמַּעֲרִיב עֲרָבִים. \\
Baruch atah, Adonai, hamaariv aravim.%
}

\newcommand{\blockB}{%
  EVER-LIVING GOD, Your majesty is proclaimed \\
by the marvels of earth and sky. \\
Sun, moon and stars testify to the power of Your wisdom. \\
Day follows day in endless succession \\
and the years vanish from our sight, \\
but Your sovereignty endures. \\
Though all things pass, \\
let not Your glory depart from our lives. \\
Help us to become co-workers with You, \\
and fill our days with abiding worth. \\
בָּרוּךְ אַתָּה, יְיָ הַמַּעֲרִיב עֲרָבִים. \\
Baruch atah, Adonai, hamaariv aravim.%
}

\newcommand{\blockC}{%
  The darkness of the first day differed from the darkness that preceded creation. The root of \\
maariv can also mean “mix," suggesting God mixed light into the primordial darkness. The \\
tiniest sparks of light can transform darkness. \\
To be "religious" might mean to have an intuitive feeling of the unity of the cosmos. ... Oneness \\
is grounded in scientific reality: we are made of the same stuff as all of creation. The deepest marvel \\
is the unity in diversity. Daniel Matt%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}