% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 13
% ==========================================
\documentclass[14pt]{extarticle}
\usepackage[paperwidth=5.5in, paperheight=8.5in, margin=0.6in]{geometry}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\setotherlanguage{hebrew}
\newfontfamily\hebrewfont[Script=Hebrew]{Ezra SIL} % Update your local system font here

% Custom page numbering to yield 13.a, 13.b, etc.
\renewcommand{\thepage}{13.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  LOVE GOD with all the power of your heart, \\
with its yearnings, its passions, \\
with all you hold dear in life, \\
and with the fullness of what the world gives you. \\
Wrap these words around your deeds as a holy garment \\
and let them shape your home into a dwelling place of peace. \\
Wherever you go scatter the words like seeds; \\
let them be drops of water on the thirsty earth. \\
Seal these words upon your heart \\
that their sacredness may permeate your being, \\
coursing through your veins, \\
melting body into soul.%
}

\newcommand{\blockB}{%
  When people come to you for help, do not turn them off with pious words, saying: "Have faith \\
and take your troubles to God!" Act instead as if there were no God, as though there were only \\
one person in all the world who could help only yourself. Martin Buber \\
Abaye said: Spread the love of God through your actions. If you yourself study and help others \\
to do so, if your business activities are decent and trustworthy, what will people say? "Have you \\
seen the behavior of one who studies Torah? How beautiful! What a fine person!" Thus Isaiah \\
(49:3) taught, “You are My servant Israel. I will be glorified through you." based on Yoma 86a%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}