% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 15
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 15.a, 15.b, etc.
\renewcommand{\thepage}{15.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  SING THE SONG of men and women \\
joined in understanding and respect. \\
The song of God's miracles, \\
an earth protected and cherished: \\
a gift for our children \\
and the generations to come. \\
The song of a land once ravished by war, \\
now quiet and content: \\
her soldiers home, to leave no more. \\
The song of a world redeemed: \\
the song of peace.%
}

\newcommand{\blockB}{%
  IN A WORLD torn by violence and pain, \\
a world far from wholeness and peace, \\
give us the courage to say, Adonai: \\
There is one God in heaven and earth. \\
The high heavens declare Your glory; \\
may earth reveal Your justice and love. \\
From bondage in Egypt, we were delivered; \\
at Sinai, we bound ourselves to Your way. \\
Inspired by prophets and instructed by sages, \\
time and again, we overcame oppressive forces. \\
Though our failings are many and our faults are great, \\
it has been our glory to bear witness to our God, \\
keeping alive in dark ages \\
Your vision of a world redeemed. \\
Let us continue to work for the day \\
when the nations will be one and at peace. \\
Then shall we rejoice as Israel did, \\
singing on the shores of the Sea:%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}