% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 5
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 5.a, 5.b, etc.
\renewcommand{\thepage}{5.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  בָּרוּךְ אַתָּה, יְיָ \\
אֱלֹהֵינוּ, מֶלֶךְ הָעוֹלָם, \\
אֲשֶׁר קִדְּשָׁנוּ בְּמִצְוֹתָיו וְצִוָּנוּ \\
עַל מִצְוַת קְרִיאַת שְׁמַע \\
לְהַמְלִיכוֹ בְּלֵבָב שָׁלֵם וּלְיַחְדוֹ \\
בְּלֵב טוֹב וּלְעָבְדוֹ בְּנֶפֶשׁ חֲפֵצָה.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  BARUCH atah, Adonai \\
Eloheinu, Melech haolam, \\
asher kid'shanu b'mitzvotav v'tzivanu \\
al mitzvat k'riat sh'ma \\
l'hamlicho b'leivav shaleim ul'yachdo \\
b'leiv tov ul'ovdo b'nefesh chafeitzah.%
}

\newcommand{\blockC}{%
  PRAISED ARE YOU, Adonai our God, Ruler of the Universe, \\
who hallows us with mitzvot, \\
commanding us how to recite the Sh'ma: \\
to declare wholeheartedly God's rule, \\
to declare earnestly God is One, \\
and to willingly worship God.%
}

\newcommand{\blockD}{%
  THREE THINGS there are together in my eye \\
that keep the thought of Thee forever nigh. \\
I think about Thy great and holy name \\
whenever I look up and see the sky. \\
My thoughts are roused to know how I was made, \\
seeing the earth's expanse where I abide. \\
The musings of my mind when I look inside \\
at all times, O my soul, "Bless Adonai!"%
}

\newcommand{\blockE}{%
  What does it mean to be called to worship? All serious activity requires preparation. The prayers \\
and blessings that precede Bar'chu are warm-ups for the individual. Now communal prayer \\
begins. The leader asks, “Are you ready to pray?" And we respond, "Yes! Let us pray!" \\
adapted from Richard Levy%
}

\newcommand{\blockF}{%
  Baruch atah, Praised are You: So important was the recitation of the Shma to our ancestors in Eretz Yisrael, that they introduced it with a blessing. That blessing fell out of use over a thousand years ago; we reclaim it here as part of our liturgical heritage. \\
There are three main avenues by which one arrives at meaning in life. The first is by creating a life or doing a deed. The second is by experiencing something or encountering someone; in other words, meaning can be found not only in work but also in love. Third: even the helpless victim of a hopeless situation, facing a fate that cannot be changed, may rise above himself, grow beyond himself, and by so doing, change himself. Viktor E. Frankl%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\blockE
\vspace{1em}
% \newpage % Uncomment to break page here

\blockF
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}