% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 166
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield 166.a, 166.b, etc.
\renewcommand{\thepage}{166.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  \begin{hebrew}
  בָּרוּךְ אַתָּה, יְיָ אֱלֹהֵינוּ \\
וֵאלֹהֵי אֲבוֹתֵינוּ וְאִמּוֹתֵינוּ, אֱלֹהֵי \\
אַבְרָהָם, אֱלֹהֵי יִצְחָק וֵאלֹהֵי יַעֲקֹב, \\
אֱלֹהֵי שָׂרָה, אֱלֹהֵי רִבְקָה, אֱלֹהֵי \\
רָחֵל וֵאלֹהֵי לֵאָה. הָאֵל הַגָּדוֹל \\
הַגִּבּוֹר וְהַנּוֹרָא, אֵל עֶלְיוֹן, גּוֹמֵל \\
חֲסָדִים טוֹבִים וְקוֹנֵה הַכֹּל, וְזוֹכֵר \\
חַסְדֵי אָבוֹת וְאִמָּהוֹת, וּמֵבִיא גְאֻלָּה \\
לִבְנֵי בְנֵיהֶם לְמַעַן שְׁמוֹ בְּאַהֲבָה. \\
*SHABBAT SHUVAH - זָכְרֵנוּ לְחַיִים, \\
מֶלֶךְ חָפֵץ בַּחַיִּים, \\
וְכָתְבֵנוּ בְּסֵפֶר הַחַיִּים, \\
לְמַעַנְךָ אֱלֹהִים חַיִים. \\
מֶלֶךְ עוֹזֵר וּמוֹשִׁיעַ וּמָגֵן. \\
בָּרוּךְ אַתָּה, יְיָ, \\
מָגֵן אַבְרָהָם וְעֶזְרַת שָׂרָה.
  \end{hebrew}%
}

\newcommand{\blockB}{%
  BARUCH atah, Adonai Eloheinu \\
v'Elohei avoteinu v'imoteinu, Elohei \\
Avraham, Elohei Yitzchak v'Elohei Yaakov, \\
Elohei Sarah, Elohei Rivkah, Elohei \\
Rachel v'Elohei Leah. Ha-El hagadol \\
hagibor v'hanora, El elyon, gomeil \\
chasadim tovim, v'koneih hakol, v'zocheir \\
chasdei avot v'imahot, umeivi g'ulah \\
livnei v'neihem I'maan sh'mo b'ahavah. \\
*SHABBAT SHUVAH - Zochreinu l'chayim, \\
Melech chafeitz bachayim, \\
v'chotveinu b'sefer hachayim, \\
I'maancha Elohim chayim. \\
Melech ozeir umoshia umagen. \\
Baruch atah, Adonai, \\
magein Avraham v'ezrat Sarah.%
}

\newcommand{\blockC}{%
  BLESSED ARE YOU, Adonai our God, God of our fathers and mothers, \\
God of Abraham, God of Isaac, and God of Jacob, \\
God of Sarah, God of Rebecca, God of Rachel, and God of Leah, \\
the great, mighty and awesome God, transcendent God \\
who bestows loving kindness, creates everything out of love, \\
remembers the love of our fathers and mothers, \\
and brings redemption to their children's children for the sake of the Divine Name. \\
*Shabbat SHUVAH - Remember us for life, O Sovereign who delights in life, \\
and inscribe us in the Book of Life, for Your sake, Living God. \\
Sovereign, Deliverer, Helper and Shield, \\
Blessed are You, Adonai, Sarah's Helper, Abraham's Shield. \\
בָּרוּךְ אַתָּה, יְיָ, מָגֵן אַבְרָהָם וְעֶזְרַת שָׂרָה. \\
Baruch atah, Adonai, magein Avraham v'ezrat Sarah.%
}

\newcommand{\blockD}{%
  *SHABBAT SHUVAH: The Shabbat between Rosh HaShanah and Yom Kippur. \\
For those who choose: At the beginning and end of the blessing, one bends the knees and bows \\
from the waist at the word Baruch and stands straight at the word " Adonai. \\
Avot v'imahot... As God has been gracious to our forebears, so may we receive \\
divine favor.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\blockC
\vspace{1em}
% \newpage % Uncomment to break page here

\blockD
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}