% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE viii
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield viii.a, viii.b, etc.
\renewcommand{\thepage}{viii.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  and the balance of particularism and universalism. But the essence of Reform liturgy \\
continues to be what God demands of us, with heavy emphasis on ethical action and \\
social justice. \\
In Beyond the Worship Wars, Thomas G. Long teaches, "Part of the joy of worship is to \\
know the motions, know the words, know the song. The vital congregations knew \\
their order of worship and moved through it with deep familiarity. What is more, the \\
worshippers had active roles - speaking, singing, moving and many of these they \\
could perform from memory." The siddur is a tool in the larger system of worship. \\
Lawrence Hoffman teaches, "The book is less text than pre-text for the staging of an \\
experience. We are returning to the age of orality, where performance of prayer \\
matters more than the fixed words. The question of worship leadership has expanded \\
now, to include the theology and artistry of being a shliach tzibur - how to \\
orchestrate seating, fill empty space, provide the right acoustics, and honor \\
individualism within the group experience." \\
Using Mishkan T'filah, the actual selection of prayer can wait for the moment. The \\
sh'liach tzibur must offer a recipe that works comfortably for the community, and be \\
able to adapt each week to the particular needs of the community, and to individuals \\
within that community. \\
Mishkan T'filah invites familiarity, even as it allows for diversity. Over time, one \\
cannot help but memorize the book. The content of each page spread, though varied, \\
becomes known. The constancy of the keva text (the right hand side of each page \\
which offers the traditional prayer) anchors every creative prayer on the left. It is the \\
cumulative effect of worshipping from this siddur that will deepen meaningful ritual. \\
The publication of Mishkan T'filah continues the Reform movement's tradition of \\
liturgical innovation. A single prayer book provides an important vehicle for group \\
identification as well as personal prayer. The Union Prayer Book and its successor Gates \\
of Prayer and now Mishkan T'filah each expresses the ethos and values of its own era, \\
at the same time being fully rooted in the structure and substance of the historical \\
liturgical tradition of the Jewish people. \\
The title Mishkan T'filah is drawn from Exodus 25:8 where God commands us to \\
build a portable sanctuary that can accompany us on our wanderings. “And let them \\
build Me a sanctuary that I may dwell among them." Mishkan T'filah is a dwelling \\
place for \\
prayer, one that moves with us wherever we might be physically or \\
spiritually. It offers the opportunity for God, the individual and community to meet.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}