% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE 124
% ==========================================
\documentclass[14pt]{extarticle}
\usepackage[paperwidth=5.5in, paperheight=8.5in, margin=0.6in]{geometry}
\usepackage{polyglossia}
\setdefaultlanguage{english}
\setotherlanguage{hebrew}
\newfontfamily\hebrewfont[Script=Hebrew]{Ezra SIL} % Update your local system font here

% Custom page numbering to yield 124.a, 124.b, etc.
\renewcommand{\thepage}{124.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  WE ENTER THIS SANCTUARY to welcome Shabbat. \\
Within these walls we sit surrounded by numberless generations. \\
Our ancestors built the synagogue as a visible sign of God's Presence in their midst. \\
Throughout our long history and our endless wanderings, it has endured, \\
a beacon of truth, love, and justice for all humanity. \\
Its presence guided our ancestors to lives of righteousness, \\
holding up to them a vision of their truest selves. \\
Now we, in our turn, come into this sanctuary to affirm the sacredness of our lives. \\
May we enter this place in peace. \\
May holiness wrap around us as we cross its threshold. \\
Weariness, doubt, the flaws within our human hearts, \\
the harshness of the week - let these drop away at the door. \\
In the brightness of Shabbat, let peace settle upon us as we lift our hearts in prayer.%
}

\newcommand{\blockB}{%
  MAY THE DOOR of this synagogue be wide enough \\
to receive all who hunger for love, all who are lonely for friendship. \\
May it welcome all who have cares to unburden, \\
thanks to express, hopes to nurture. \\
May the door of this synagogue be narrow enough \\
to shut out pettiness and pride, envy and enmity. \\
May its threshold be no stumbling block \\
to young or straying feet. \\
May it be too high to admit complacency, \\
selfishness and harshness. \\
May this synagogue be, for all who enter, \\
the doorway to a richer and more meaningful life.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\blockB
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}