% ==========================================
% AUTO-GENERATED STAGING FILE FOR PAGE xv
% ==========================================
\documentclass{siddur}

% Custom page numbering to yield xv.a, xv.b, etc.
\renewcommand{\thepage}{xv.\alph{page}}

% --- MACRO DEFINITIONS ---
\newcommand{\blockA}{%
  A Note on Style and Usage \\
Mishkan T'filah offers many opportunities for diverse usage and worship styles. Most \\
of the prayers in this siddur are set as a two-page spread, with the keva (primary, \\
traditional) liturgy on the right-hand page and alternative prayer choices on the left- \\
hand side. The right-hand Hebrew text is accompanied by a faithful translation, and \\
transliteration; the left-hand page contains poetry, prayers and kavanot (meditations) \\
thematically tied to the keva text but reflecting diverse theological points of view. \\
Layouts of the prayers invite different usage. Some passages are set to facilitate \\
responsive readings, though all passages allow for unison offering. It is suggested that \\
the community vary its vocal expression in prayer, with quieter or more exuberant \\
tones at appropriate moments, as guided by the worship leader. \\
The two-page spreads are intended so that only one prayer per page spread is read, \\
either in Hebrew or English. Once that single piece is prayed, the worshipper turns the \\
page. Thus pages need be announced only when they are skipped. (These simple \\
instructions at the beginning of each service will guide new worshippers.) If the \\
worship leader begins each prayer slowly, this will help worshippers to locate their \\
places easily. \\
A linear-style service option is offered in Service II for Friday night and Shabbat \\
morning. Linear pages are designed with a blue frame around the page. The English in \\
these services is not a direct translation of the Hebrew prayers. \\
To pray the most traditional liturgy, one would use the right-hand side of the two- \\
page spread of any service (except Services II). \\
"Stage directions" and choreography such as when to stand or sit are minimized for \\
maximum flexibility and with respect for varying congregational customs. \\
Spiritual commentaries, notes on rabbinic practices, and source citations span the \\
bottom of the pages, below the liturgical frame. The heading "For those who choose" \\
refers to Jewish customs established by long usage. While not binding, many \\
congregants will find them meaningful, and their use can enhance one's kavanah. Text \\
sources are abbreviated: M. Shabbat 2:1 is read as Mishnah Shabbat, chapter 2, \\
paragraph 1. Shabbat 2b-3a refers to the Talmud tractate Shabbat, page 2b to page 3a. \\
Rubric headings are on the outside margins, indicating the current prayer's place \\
within the service.%
}

% --- DOCUMENT BODY ---
\begin{document}
\blockA
\vspace{1em}
% \newpage % Uncomment to break page here

\end{document}